# Reproducible Research: Peer Assessment 1

```{r setoptions,echo=FALSE}
opts_chunk$set(echo=TRUE)
```

## Loading and preprocessing the data

Extract the data if it is not already extracted.

```{r extract}
unzip(paste("data", "activity.zip", sep="/"), exdir="data", overwrite=FALSE)
```

Read the data from the extracted file.

```{r read_data}
extracted_filename = paste("data", "activity.csv", sep="/")
raw_data = read.csv(extracted_filename)
```

## What is mean total number of steps taken per day?

Group the number of steps taken per day.

```{r steps_per_day}
steps_per_day = aggregate(steps ~ date, raw_data, sum)
```

### Histogram

```{r steps_per_day_hist}
hist(steps_per_day$steps, main="Histogram of number of steps per day", xlab="Steps per day", breaks=8)
```

### Mean

```{r steps_per_day_mean}
mean(steps_per_day$steps)
```

### Median

```{r steps_per_day_median}
median(steps_per_day$steps)
```

## What is the average daily activity pattern?

Group the number of steps taken per interval.

```{r steps_per_interval}
data_without_na = subset(raw_data, !is.na(raw_data$steps))
steps_per_interval = aggregate(steps ~ interval, data_without_na, mean)
```

Plot the data.

```{r steps_per_interval_plot}
plot(steps_per_interval$interval, steps_per_interval$steps, type="l")
```

The time interval, on average across all the day in the dataset, that contains
the maximum number of steps is:

```{r max_interval}
row_with_most_average_steps <- which.max(steps_per_interval$steps)
steps_per_interval[row_with_most_average_steps,]$interval
```

## Imputing missing values


## Are there differences in activity patterns between weekdays and weekends?
