# Reproducible Research: Peer Assessment 1

```{r setoptions,echo=FALSE}
opts_chunk$set(echo=TRUE)
```

## Loading and preprocessing the data

Extract the data if it is not already extracted.

```{r extract}
unzip(paste("data", "activity.zip", sep="/"), exdir="data", overwrite=FALSE)
```

Read the data from the extracted file.

```{r read_data}
extracted_filename = paste("data", "activity.csv", sep="/")
raw_data = read.csv(extracted_filename)
```

## What is mean total number of steps taken per day?

Group the number of steps taken per day.

```{r steps_per_day}
steps_per_day = aggregate(steps ~ date, raw_data, sum)
```

### Histogram

```{r steps_per_day_hist}
hist(steps_per_day$steps, main="Histogram of number of steps per day", xlab="Steps per day", breaks=8)
```

### Mean

```{r steps_per_day_mean}
mean(steps_per_day$steps)
```

### Median

```{r steps_per_day_median}
median(steps_per_day$steps)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
