# Reproducible Research: Peer Assessment 1

```{r setoptions,echo=FALSE}
opts_chunk$set(echo=TRUE)
library(lattice)
```

## Loading and preprocessing the data

Extract the data if it is not already extracted.

```{r extract}
unzip(paste("data", "activity.zip", sep="/"), exdir="data", overwrite=FALSE)
```

Read the data from the extracted file.

```{r read_data}
extracted_filename = paste("data", "activity.csv", sep="/")
raw_data = read.csv(extracted_filename)
```

## What is mean total number of steps taken per day?

Group the number of steps taken per day.

```{r steps_per_day}
steps_per_day = aggregate(steps ~ date, raw_data, sum)
```

### Histogram

```{r steps_per_day_hist}
hist(steps_per_day$steps, main="Histogram of number of steps per day", xlab="Steps per day", breaks=8)
```

### Mean

```{r steps_per_day_mean}
mean(steps_per_day$steps)
```

### Median

```{r steps_per_day_median}
median(steps_per_day$steps)
```

## What is the average daily activity pattern?

Group the number of steps taken per interval.

```{r steps_per_interval}
data_without_na = subset(raw_data, !is.na(raw_data$steps))
steps_per_interval = aggregate(steps ~ interval, data_without_na, mean)
```

Plot the data.

```{r steps_per_interval_plot}
plot(steps_per_interval$interval, steps_per_interval$steps, type="l")
```

The time interval, on average across all the day in the dataset, that contains
the maximum number of steps is:

```{r max_interval}
row_with_most_average_steps <- which.max(steps_per_interval$steps)
steps_per_interval[row_with_most_average_steps,]$interval
```

## Imputing missing values

The number of rows that don't have steps:

```{r na_count}
nrow(subset(raw_data, is.na(raw_data$steps)))
```

The NA values will be imputed using the mean number of steps per interval for
the day:

```{r mean_steps}
mean_steps <- mean(data_without_na$steps)
imputed_data <- raw_data
imputed_data$steps[is.na(imputed_data$steps)] <- mean_steps
imputed_steps_per_day = aggregate(steps ~ date, imputed_data, sum)
```

### Histogram

```{r imputed_steps_per_day_hist}
hist(imputed_steps_per_day$steps, main="Histogram of number of steps per day", xlab="Steps per day", breaks=8)
```

### Mean

```{r imputed_steps_per_day_mean}
mean(imputed_steps_per_day$steps)
```

### Median

```{r imputed_steps_per_day_median}
median(imputed_steps_per_day$steps)
```

When compared with the mean and median of the raw data, this doesn't affect
the output hardly at all. That is not what I was expecting.

When comparing the histogram of the imputed values, the histogram does show an
increase in days that have 10,000 steps. I think this makes sense because if
you look at the original histogram of the raw data, it seems not to be a pure
bell curve, but shifted to emphasize the 10,000 step section. With the imputed
data, the days where the person fell short of the 10,000 step goal are being
pushed over the top by the imputed values.

## Are there differences in activity patterns between weekdays and weekends?

Add a weektime factor to the dataset.

```{r week_data}
week_data = data_without_na
week_data$weektime <- as.factor(
        ifelse(weekdays(as.Date(week_data$date)) %in% 
                       c("Saturday","Sunday"), "weekend", "weekday"))
steps_per_weektime = aggregate(steps~interval+weektime, week_data, mean)
```

Plot weekdays versus weekends.

```{r weekdays_versus_weekends}
xyplot(steps ~ interval | weektime, data=steps_per_weektime, type="l",
       ylab="Number of steps")
```